Estimating real-time highstreet footfall from Wi-Fi probe requests

### 2018-06-26 paper/sections/main_study.tex
analysis

\begin{figure}
	\begin{center}
		\includegraphics [width=\linewidth] {images/main_schedule.jpeg}
		\caption{Clustering probe requests based on increasing sequence numbers present in them. The dots are individual probe requests and the red lines connect probe requests within the same cluster which are generated by the same mobile device.}
		\label{pilot_clustering}
	\end{center}
\end{figure}

\begin{table}
	\tbl{Locations where sensors were installed}
	{\begin{tabular}{clll} 
		\toprule
		 ID & Location & Type & Installation notes\\
		 \midrule
		 1 & Camden High Street & Phone Shop & Bus stop in front\\
		 2 & Central St.Giles Piazza & Restaurant & Seating area on both sides\\
		 3 & Holborn Underground Station & Information Kiosk & Overlooks station entrance\\
		 4 & Brunswick Center & Fast Food Restaurant & Has seating area on one side\\
		 5 & The Strand & Regular Shop & Has phone shop next door \\
		 \bottomrule
	\end{tabular}}
	% \tabnote{\textsuperscript{a}This footnote shows how to include footnotes to a table if required.}
	\label{locations-table}
\end{table}

\begin{figure}
	\centering
	\subfigure[Distribution of signal strengths showing the filtering of background noise]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 6 20 6,clip]{images/main_configs.jpeg}}}\hspace{20pt}
	\subfigure[Clustering probe requests as nodes in a graph using increasing sequence numbers]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 6 25 6,clip]{images/main_signals.jpeg}}}
	\caption{Schematic diagrams explaining the methods for filtering by signal strength and clustering using sequence numbers} \label{methodology_schematic}
\end{figure}

@@

We do a daily analysis of distribution of signal strengths.
The thresholds are shown in the table.
The average is xxxx and standard deviation is xxx.
we notice that the variation is lot. There is a definite
change with the micro site locations.

We see how the signal strength filtering affects the counts.
compared to manual counts we look at the average mean errors (daily)
per 5 minutes. The counts go as follows.
Shown as a red line in the Figure.

We can conclude that even though it has variations, this is
a good method to reduce the overall level of error.

>>>>

\begin{table}
	\tbl{Locations where sensors were installed}
	{\begin{tabular}{clll} 
		\toprule
		 ID & Location & Type & Installation notes\\
		 \midrule
		 1 & Camden High Street & Phone Shop & Bus stop in front\\
		 2 & Central St.Giles Piazza & Restaurant & Seating area on both sides\\
		 3 & Holborn Underground Station & Information Kiosk & Overlooks station entrance\\
		 4 & Brunswick Center & Fast Food Restaurant & Has seating area on one side\\
		 5 & The Strand & Tea Shop & Has phone shop next door \\
		 \bottomrule
	\end{tabular}}
	\label{locations-table}
\end{table}

\begin{figure}
	\begin{center}
		\includegraphics [width=0.90\linewidth] {images/main_schedule.jpeg}
		\caption{Days when the sensors were active at the corresponding location. The red square shows that manual data collection was also done.}
		\label{pilot_clustering}
	\end{center}
\end{figure}

Though data was collected for many continous days, for the purposes of comparing with ground truth we just consider the only the data from sensors corresponding to those sessions. We have 12 sets of data over 6 different days. We have atleast two set manual counts for each location for verification of calibration.

\subsection{signal strength filtering}
First we see the distribution of the signal strength varies with location and configuration. 
The density plot for signal strength is shown alogn with configuration in figure.
We can see that the signal strength distribution shows distinct patterns of high and low when the installation is that there is a clear distant source of noise but this distinction get more and more obscure as we move towards difficult installations. 
For example, location 2 is almost a normally distributed noise as it is too far to pick up any pedestrians but location 5 with a clear view of footpath and a phone shop next door shows clear distinction between the two. 
Intuitively the classfication algorithm should give us better results in the latter. 
It is important to note that we are dealing with relative singal strengths, this can vary with location and time of the analysis but we should be still be able to differentiate signal from noise. 
We run the kmeans classification algorithm and filter out the probe requests which are randomised and have signal strengths less than the second break (or the threshold). 
We then count the number of Unique MAC addresses present in every minute and remove MAC addreses which reappear within 30 minutes of previous appearance. 
We then compare this with the minute by minute aggreagation for the manual counts and find the average error per minute for the sensor count. 
The results are shown in the table.We see that the location XXXX has the most error while location XXX has the least error confirming our intuition. 
We also see that the error follows the complexity of the installation. 
It is also very promising that this method alone reduces our margin of error by a lot. 
For some practical purposes which does not require absolute numbers, this should be sufficient. talk about examples of indexes and dashboards and short term trends.

\begin{figure}
	\centering
	\subfigure[Installation configuration of sensors at various locations]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 6 20 6,clip]{images/main_configs.jpeg}}}\hspace{20pt}
	\subfigure[Density distribution of signal strength (lower values show higher signal strength)]{
		\resizebox*{0.46\linewidth}{!}{\includegraphics[trim=20 4 25 6,clip]{images/main_signals.jpeg}}}
	\caption{Distribution of signal strengths across locations} \label{methodology_schematic}
\end{figure}

@@
